\section{快速开始}

The way we think about programming has undergone many changes in the years since the first electronic computers required patch cables and switches to convey instructions from human to machine. As is the case with many aspects of society, changes in computing technology provide computer scientists with a growing number of tools and platforms on which to practice their craft. Advances such as faster processors, high-speed networks, and large memory capacities have created a spiral of complexity through which computer scientists must navigate. Throughout all of this rapid evolution, a number of basic principles have remained constant. The science of computing is concerned with using computers to solve problems.

自计算机通过电缆和交换机来传递人的指令起，人们对编程的看法就发生了许多变化。与社会的许多方面一样，计算技术的变化为计算机科学家提供了越来越多的工具和平台来实践他们的工艺。计算机的快速发展，诸如快速处理器、高速网络和大存储器容量已经让计算机科学家陷入高度复杂螺旋中。在所有这些快速演变中，一些基本原则保持不变。计算机科学关注用计算机来解决问题。


You have no doubt spent considerable time learning the basics of problem-solving and hopefully feel confident in your ability to take a problem statement and develop a solution. You have also learned that writing computer programs is often hard. The complexity of large problems and the corresponding complexity of the solutions can tend to overshadow the fundamental ideas related to the problem-solving process.

或许你花了很多时间学习了解决问题的基础知识，希望自己能把问题弄清楚并提出解决方案。接着你可能还会发现编程有些难。问题以及解决方案的复杂性可能会掩盖求解过程中的一些基本思想。

%毫无疑问你花了相当多的时间学习解决问题的基础知识，以此希望有足够的能力把问题弄清楚并想出解决方案。你还发现编写代码通常很困难。问题的复杂性和解决方案的相应复杂性往往会掩盖与解决问题过程相关的基本思想。


This chapter emphasizes two important areas for the rest of the text. First, it reviews the framework within which computer science and the study of algorithms and data structures must fit, in particular, the reasons why we need to study these topics and how understanding these topics helps us to become better problem solvers. Second, we review the Python programming language. Although we cannot provide a detailed, exhaustive reference, we will give examples and explanations for the basic constructs and ideas that will occur throughout the remaining chapters.

本章的其余部分将着重介绍两个重要的领域。首先回顾一下计算机科学与研究算法和数据结构所必须适应的框架，特别是我们需要研究这些主题的原因，以及如何理解这些主题有助于我们更好的解决问题。其次我们将回顾 Python 编程语言。这里不提供详尽的参考，但我们将在其余章节中给出基本数据结构的示例和解释。 
